---
title: "Predicting profitability in R"
author: "Joan Claverol - Data analytics mentor"
output:
  ioslides_presentation:
    background: white
    smaller: yes
    widescreen: yes
    css: https://maxcdn.bootstrapcdn.com/bootstrap/3.3.7/css/bootstrap.min.css
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, cache = F)
```

```{r loading libraries and dataset, message=FALSE, warning=F}
if(require("pacman")=="FALSE"){
  install.packages("pacman")
} 

pacman::p_load(corrplot, dplyr, ggplot2, caret, tidyr, dunn.test, Hmisc,xtable, htmlTable, 
               knitr, kableExtra, RColorBrewer, e1071, FNN, scales,
               tibble, modelr, magrittr, VIM, fastDummies, plotly, readr)

ex_prod <- read_csv("../data/existingproductattributes2017.2.csv")
new_prod <- read_csv("../data/newproductattributes2017.2.csv")
```

## Task overview

**BUSINESS QUESTION:** Which are the top 5 products that are going to be more profitable for the company?

What data do we have? 

New product attributes and existing product attributes.

- Predicting sales of four different product types: PC, Laptops, Netbooks and Smartphones
- Assessing the impact services reviews and customer reviews have on sales of different product types

## Index

1. Data cleaning

2. Data exploration

3. Pre-process: feature selection (correlation matrix) & feature engineering

4. Modalization: linear regresion, KNN, SVM and Random forest

5. Error analysis

## Exploring the data 

```{r summary of the data}
glimpse(ex_prod)
```


## Data cleaning

Transformation to factor:

```{r transformation to factors, echo=TRUE}
fact_var <- c("ProductType","ProductNum")
ex_prod[,fact_var] <- apply(ex_prod[,fact_var], 2, as.factor)
```

Giving names to the rows: 

```{r changing row names with product number, echo=TRUE}

ex_prod <- tibble::column_to_rownames(.data = ex_prod,
                                     var = "ProductNum")
ex_prod$ProductNum <- NULL
```

## Data cleaning: detecting NA with VIM of Best Seller Rank {.flexbox .vcenter}

```{r looking for NAs, message=F, warning=F}
aggr(ex_prod, col=c('lightblue','red'), numbers=TRUE, sortVars=TRUE, 
     labels=names(data), cex.axis=.7,  gap=3, only.miss = F, 
     ylab=c("Histogram of missing data","Pattern"),plot = T)
# change blue color
ex_prod$BestSellersRank <- NULL
```

## 1st data expl.: [Blackwell business](http://rpubs.com/JoanClaverol/493693) {.flexbox .vcenter}

```{r business overview, warning=F}
# Is the volume related to the categories?
ex_prod %>%
  group_by(ProductType) %>%
  summarise(
    Total_Volume = sum(Volume), 
    Number_Products = n(),
    Median_Profit_Perc = round(median(ProfitMargin),2),
    Median_Price_Perc = round(median(Price) ,2)
    ) %>%
  mutate(
    Total_Profits = Median_Profit_Perc*Median_Price_Perc*Total_Volume,
    Total_Profits_Dol = paste(round((Total_Profits), 0),"$")
    ) %>% 
  arrange(desc(Total_Volume)) -> categories_analysis 

categories_analysis %>% 
  ggplot(aes(x = reorder(ProductType, Total_Profits))) +
    geom_col(aes(y = Total_Profits), fill = "gold") +
    geom_col(aes(y = -Total_Volume), fill = "dodgerblue3") +
    coord_flip() +
    scale_y_continuous(limits = c(-80000, 650000), labels = NULL) +
    geom_label(aes(x = ProductType, y = Total_Profits, 
                   label = Total_Profits_Dol),
               hjust = 0, 
               vjust = 0.4, 
               colour = "goldenrod3", 
               fill = NA, 
               label.size = NA, 
               size = 3.5) +
    geom_label(aes(x = ProductType, y = -Total_Volume, 
                   label = round(Total_Volume, 0)),
               hjust = 1, 
               vjust = 0.4, 
               colour = "dodgerblue4", 
               fill = NA, 
               label.size = NA, 
               size = 3.5) +
    labs(title = "Blackwell overview",
         subtitle = "Total Volume (items) vs Total Profits ($)") +
    theme(legend.position = "bottom", 
          legend.title = element_blank(), 
          plot.title = element_text(hjust = 0.5), 
          plot.subtitle = element_text(hjust = 0.5)) + theme_void() -> p1
p1 + theme(axis.title.x = element_blank(), 
           axis.title.y = element_blank(), 
           axis.text.y = element_text())
  # geom_label(aes(x = "Printer", y = 10000, 
  #                label = "The 45% of the sales comes from\naccessories, but they only\nrespresents the 15% of the total\nprofit"),
  #            hjust = 0, 
  #            vjust = 0.5, 
  #            lineheight = 0.8,
  #            colour = "dodgerblue4", 
  #            fill = "white", 
  #            label.size = NA, 
  #            size = 4.5) +
  # geom_label(aes(x = "Laptop", y = 10000, 
  #                label = "Extended warranty generates the\n46% of the total profit, and\nrepresents the 18% of the sales"),
  #            hjust = 0, 
  #            vjust = 0.5, 
  #            lineheight = 0.8,
  #            colour = "goldenrod3", 
  #            fill = "white", 
  #            label.size = NA, 
  #            size = 4.5)
  
```

## 1st data expl.: Volume distribution {.flexbox .vcenter}

```{r boxplot to understand the distribution of the volume, warning=FALSE, message=FALSE}
# creating a function to find outliers
is_outlier <- function(x) {
  return(x < quantile(x, 0.25) - 1.5 * IQR(x) | x > quantile(x, 0.75) + 1.5 * IQR(x))
}

# creating the graphs
ex_prod %>% 
  rownames_to_column(var = "productNum") %>% 
  group_by(ProductType) %>%
  mutate(outlier=ifelse(is_outlier(Volume),as.numeric(productNum),
                        as.numeric(NA))) %>%
  ggplot(aes(ProductType, Volume)) + 
    geom_boxplot(outlier.color = "red", col = "dodgerblue3") +
    geom_label(aes(label = outlier), hjust = 0, 
               vjust = 0, check_overlap = TRUE,
               colour = "red", 
               fill = NA, 
               label.size = NA, 
               size = 3.5) +
    geom_label(aes(x = "Laptop", y = 10000, 
                   label = "Accessories: median very close to 0, and the product\n150 is an anomaly."), 
               label.size = NA, 
               size = 4.5, 
               colour = "#555555", 
               hjust = 0, 
               vjust = 0.5, 
               lineheight = 0.8) +
    geom_label(aes(x = "Laptop", y = 8000, 
                   label = "Extended warranty: the range is very gathered and\nthere are two products, 132 and 133, close to 0."), 
               label.size = NA, 
               size = 4.5, 
               colour = "#555555", 
               hjust = 0, 
               vjust = 0.5, 
               lineheight = 0.8) +
    geom_label(aes(x = "Laptop", y = 6000, 
                   label = "GameConsole: the highest sells in the company and\nmore stable."), 
               label.size = NA, 
               size = 4.5, 
               colour = "#555555", 
               hjust = 0, 
               vjust = 0.5, 
               lineheight = 0.8) +
    labs(title = "Volume distribution in relation to product type") +
    theme_classic() + 
    theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 11), 
          axis.text.y = element_text(size = 11), legend.position = "none",
          axis.title.x = element_blank(), axis.title.y = element_blank())
```

## 1st modalization: linear regression {.flexbox .vcenter}

```{r 1st model creatin, warning=F, message=F, echo=T}
# train and test
train_id <- createDataPartition(y = ex_prod$Volume, p = 0.80, list = F)
train <- ex_prod[train_id,]
test <- ex_prod[-train_id,]

# create linear regression model
mod_lm <- lm(formula = Volume ~ ., data = train)
```

```{r results 1st model, message=F, warning=F}
# model performance
train_res_mod1 <- postResample(pred = predict(object = mod_lm, newdata = train),
                             obs = train$Volume)
results_mod1 <- postResample(pred = predict(object = mod_lm, newdata = test),
                             obs = test$Volume)

# creating a grid with the different results
table_mod1 <- tribble(~metric,   ~train           ,        ~test     , 
                      "RMSE" , round(train_res_mod1[[1]],2), round(results_mod1[[1]],2),      
                      "R^2"  , paste(round(train_res_mod1[[2]]*100,2),"%"), paste(round(results_mod1[[2]]*100,2),"%"))
kable(table_mod1) %>% 
  kable_styling(bootstrap_options = c("hover"), 
                full_width = F, position = "center", fixed_thead = T)
```

Main predictors: 

1. 5 stars
2. Product type: Game console

## 2nd pre-process: feature selection {.flexbox .vcenter}

```{r}
# Dummy variables 
ex_prod_dummy <- ex_prod %>% 
  fastDummies::dummy_columns(remove_first_dummy = FALSE) %>% 
  select(-ProductType, -ShippingWeight, -ProductDepth,
         -ProductWidth, -ProductHeight, -ProductType_Accessories,
         -ProductType_Software, -ProductType_Display, -ProductType_Printer,
         -ProductType_PrinterSupplies, -ProductType_ExtendedWarranty,
         -ProductType_Tablet, -ProductType_GameConsole) %>% 
  rename(PC = ProductType_PC, 
         Laptop = ProductType_Laptop,
         Netb = ProductType_Netbook,
         Smart_Ph = ProductType_Smartphone, 
         x5 = x5StarReviews, 
         x4 = x4StarReviews,
         x3 = x3StarReviews, 
         x2 = x2StarReviews, 
         x1 = x1StarReviews, 
         Pos_Ser = PositiveServiceReview, 
         Neg_Ser = NegativeServiceReview,
         Recomend = Recommendproduct,
         Profit_M = ProfitMargin,
         Vol = Volume)
rownames(ex_prod_dummy) <- rownames(ex_prod)


# Correlation plot
ex_prod_corr <- cor(ex_prod_dummy)
corrplot(ex_prod_corr, method = "pie", 
         type = "lower", order = "FPC", 
         col = brewer.pal(n = 8, name = "RdBu"),
         number.cex = 0.9, number.digits = 2, 
         tl.cex = 1.2, tl.srt = 1, tl.col = "black")
```

## 2nd modalization: linear regression {.bigger .flexbox .vcenter}

```{r 2nd model creation, warning=FALSE, message=FALSE}
# creating trainin and testing with the features selected
set.seed(123)
train_id <- createDataPartition(y = ex_prod_dummy$Vol,
                                p = 0.80,
                                list = F)
train <- ex_prod_dummy[train_id,]
test <- ex_prod_dummy[-train_id,]

# model creation
mod_2lm <- lm(formula = Vol ~., data = train)

# model performance
train_res_mod2 <- postResample(pred = predict(object = mod_2lm, newdata = train),
                             obs = train$Vol)
results_mod2 <- postResample(pred = predict(object = mod_2lm, newdata = test),
                             obs = test$Vol)

# creating a grid with the different results
table_mod2 <- tribble(~metric,   ~train           ,        ~test     , 
                        "RMSE" , round(train_res_mod2[[1]],2), round(results_mod2[[1]],2),      
                        "R^2"  , paste(round(train_res_mod2[[2]]*100,2),"%"), paste(round(results_mod2[[2]]*100,2),"%"))
kable(table_mod2) %>% 
  kable_styling(bootstrap_options = c("hover"), 
                full_width = F, position = "center", fixed_thead = T)
```

Main predictors: 

1. 5 stars
2. Product type: PC
3. Price

The model is overfitted again. 

## 3rd pre-process: outliers in stars features{.flexbox .vcenter}

```{r plot the stars volume relation, warning=F, message=F}
ex_prod_dummy %>%
  rownames_to_column(var = "product_num") %>%
  gather(key = "star_type", value = "num_stars", x5, x4, x3, x2, x1) %>% 
  ggplot(aes(x = num_stars, y = Vol, color = star_type)) +
    geom_point() +
    geom_smooth(se = F, size = 0.15) +
    theme_classic() +
    theme(axis.text.y = element_text(),
          axis.text.x = element_text(), 
          legend.title = element_blank()) +
    labs(title = "Total sales vs type of star", 
         y = "Volume", x = "Number of stars") -> stars_plot
ggplotly(stars_plot) %>% 
  layout(annotations = list(x = 2801, y = 11204, text = "Prod. 150", 
                            showarrow = TRUE, arrowcolor = "#555555",
                            arrowsize = 0.3, font = list(size = 10))) %>% 
  layout(annotations = list(x = 1759, y = 7036, text = "Prod. 198", 
                            showarrow = TRUE, arrowcolor = "#555555",
                            arrowsize = 0.3, font = list(size = 10), 
                            ax= 0, ay = -20)) %>%
  layout(annotations = list(x = 1654, y = 2052, text = "Prod. 123", 
                            showarrow = TRUE, arrowcolor = "#555555",
                            arrowsize = 0.3, font = list(size = 10),
                            ax = 10, ay = 20))
  
```

```{r outlier extraction}
ex_prod_dummy %<>%
  rownames_to_column(var = "product_num") %>% 
  filter(!(product_num %in% c("123","198","150")))
```

## 3rd pre-process: feature engineering {.flexbox .vcenter}

```{r volumen total stars relation, message=F, warning=F}
# 
ex_prod_dummy %<>% 
  rowwise() %>% 
  mutate(total_stars = sum(x5, x4, x3, x2, x1)) 

ex_prod_dummy %>% 
  ggplot(aes(x = total_stars, y = Vol)) +
    geom_point(color = "dodgerblue4") +
    geom_smooth(alpha=0.3, size=0, span=0.5, se = F) +
    geom_label(aes(x = 650, y = 900, 
                   label = "There is a clear positive correlation\nbetween the total number of stars\na product has with the number of sales"),
             hjust = 0, 
             vjust = 0.5, 
             lineheight = 0.8,
             colour = "#555555", 
             fill = "white", 
             label.size = NA, 
             size = 4.5 ) +
    theme_classic() +
    theme(axis.text.y = element_text(),
          axis.text.x = element_text(), 
          legend.title = element_blank()) +
    labs(title = "Total sales vs total number of stars by product", 
         y = "Volume", x = "total number of stars")
```

## 3rd pre-process: corr. matrix with total stars {.flexbox .vcenter}

```{r}
# Correlation plot
ex_prod_corr <- cor(ex_prod_dummy %>% 
                      select(-product_num, -x5, -x4, -x3, -x2, -x1, 
                             -Profit_M, -Price))
corrplot(ex_prod_corr, method = "pie", 
         type = "lower", order = "FPC", 
         col = brewer.pal(n = 8, name = "RdBu"),
         number.cex = 0.9, number.digits = 2, 
         tl.cex = 1.2, tl.srt = 1, tl.col = "black")
```

## 3rd pre-process: corr. matrix with x4 and x2 {.flexbox .vcenter}

```{r}
# Correlation plot
ex_prod_corr <- cor(ex_prod_dummy %>% 
                      select(-product_num, -x5, -x3, -x1, -total_stars, 
                             -Profit_M, -Price))
corrplot(ex_prod_corr, method = "pie", 
         type = "lower", order = "FPC", 
         col = brewer.pal(n = 8, name = "RdBu"),
         number.cex = 0.9, number.digits = 2, 
         tl.cex = 1.2, tl.srt = 1, tl.col = "black")
```

## 3rd modalization: linear regression {.flexbox .vcenter}

```{r 3rd model with linear regression}
ex_prod_dummy %<>% 
  select(-x5, -x3, -x1, -total_stars, -Profit_M, -Price) %>% 
  column_to_rownames(var = "product_num")

# creating trainin and testing with the features selected
set.seed(123)
train_id <- createDataPartition(y = ex_prod_dummy$Vol,
                                p = 0.80,
                                list = F)
train <- ex_prod_dummy[train_id,]
test <- ex_prod_dummy[-train_id,]

# model creation
mod_3lm <- lm(formula = Vol ~., data = train)

# model performance
train_res_mod3 <- postResample(pred = predict(object = mod_3lm, newdata = train),
                             obs = train$Vol)
results_mod3 <- postResample(pred = predict(object = mod_3lm, newdata = test),
                             obs = test$Vol)

# creating a grid with the different results
table_mod3 <- tribble(~metric,   ~train           ,        ~test     , 
                        "RMSE" , round(train_res_mod3[[1]],2), round(results_mod3[[1]],2),      
                        "R^2"  , paste(round(train_res_mod3[[2]]*100,2),"%"), paste(round(results_mod3[[2]]*100,2),"%"))
kable(table_mod3) %>% 
  kable_styling(bootstrap_options = c("hover"), 
                full_width = F, position = "center", fixed_thead = T)
```

My model is not overfitted, but has a very low performance. Let's check where it is failing!

## 3rd error check: errors visualization lm {.flexbox .vcenter}

```{r error visualization 3rd model, warning=FALSE}
# adding product number to datasets and creating one only with categories
ex_prod$product_num <- rownames(ex_prod)
ex_prod_dummy$product_num <- rownames(ex_prod_dummy)
product_cat <- ex_prod %>% select(product_num, ProductType)

# define the treshold of the errors and relevant categories
treshold <- 80
rel_categories <- c("PC","Laptop","Smartphone","Netbooks")

# looking at the metrics of the relevant categories
ex_prod_dummy %<>%
  left_join(y = product_cat, by = "product_num") %>% 
  add_predictions(model = mod_3lm, var = "pred") %>% 
  add_residuals(model = mod_3lm, var = "resid")

ex_prod_dummy %>% 
  dplyr::filter(ProductType %in% rel_categories) -> ex_prod_filt

metrics_rel_prod <- postResample(pred = ex_prod_filt$pred, obs = ex_prod_filt$Vol)
#        RMSE    Rsquared         MAE 
# 117.8325360   0.9455967  82.2058960 

# error plot
ex_prod_dummy %>% 
  ggplot(aes(x = pred, y = Vol)) +
    geom_point(aes(color = (ProductType %in% rel_categories))) + 
    geom_abline(intercept = 0, slope = 1, color = "darkgray") +
    geom_label(aes(label = if_else(abs(resid)>treshold & 
                              ProductType %in% rel_categories, 
                              paste(ProductType, product_num), NULL)),
               hjust = 0, 
               vjust = 0.4, 
               colour = "red2", 
               fill = NA, 
               label.size = NA, 
               size = 3.5) +
    geom_label(aes(x = -300, y = 2000,
                   label = paste0("The metrics for the relevant product types are:\n   - RMSE: ",
                                  round(metrics_rel_prod[[1]],3),"\n   - Rsquared: ",
                                  round(metrics_rel_prod[[2]],3),"\n   - MAE: ",
                                  round(metrics_rel_prod[[3]],3))),
               label.size = NA,
               size = 4.5,
               colour = "red2",
               hjust = 0,
               vjust = 0.5,
               lineheight = 0.8) +
    labs(title = "Error visualizations 3rd model (lm)",
         x = "Predicted volume",
         y = "Volume") +
    scale_color_manual(values = c("grey","red")) +
    theme_classic() +
    theme(axis.text.y = element_text(),
          axis.text.x = element_text(), 
          legend.title = element_blank(), 
          legend.position = "none") -> error_plot_mod3
error_plot_mod3
```

## 4th exploration: recommandation variable {.flexbox .vcenter}

```{r recommendation variable exploration, warning=F, message=F}
ex_prod_dummy %>% 
  group_by(as.factor(Recomend)) %>% 
  mutate(outlier=ifelse(is_outlier(Vol),as.numeric(product_num),
                        as.numeric(NA))) %>%
  ggplot(aes(x = as.factor(Recomend), y = Vol)) + 
    geom_boxplot(outlier.color = "red", col = "dodgerblue3") +
    geom_label(aes(label = outlier), hjust = 0, 
               vjust = 0, check_overlap = TRUE,
               colour = "red", 
               fill = NA, 
               label.size = NA, 
               size = 3.5) +
    geom_label(aes(x = "0.1", y = 2000, 
                   label = "There is an increase of the range related to the increment\nof the % recommendation. Problem: Big dispersion for higer rates.\n100% recommendation has 0 volume."), 
               label.size = NA, 
               size = 3.5, 
               colour = "#555555", 
               hjust = 0, 
               vjust = 0.5, 
               lineheight = 0.8) +
    theme_classic() +
    labs(title = "Distribution of the volume for each recommendation",
         x = "% of product recommendation", y = "Volume")
```

## 4th pre-process: repeated observations {.flexbox .vcenter}

```{r identifying repeated rows, warning=F, message=F}
kable(ex_prod_dummy %>% 
  select(product_num, ProductType, Pos_Ser, Neg_Ser, Recomend, Vol) %>% 
  filter(ProductType %in% c("ExtendedWarranty")), format = "html") %>% 
  kable_styling(bootstrap_options = c("hover"), 
                full_width = T, position = "center", fixed_thead = T) %>% 
  row_spec(3:10, bold = T, background = "#f0f5f0")

ex_prod_dummy %<>% 
  dplyr::distinct(ProductType, Pos_Ser, Neg_Ser, Recomend, Vol, 
                  .keep_all = TRUE)
```

## 4th feature engineering: pos. and neg. service {.flexbox .vcenter}

```{r negative and positive service vs volume, warning=F, message=F}
ex_prod_dummy %>% 
  gather(key = "service_type", value = "service_quantity", Pos_Ser, Neg_Ser) %>% 
  ggplot(aes(y = Vol, x = service_quantity, color = service_type)) +
    geom_point(alpha = 0.35) +
    geom_smooth(se = F, size = 0.15) +
    labs(title = "Total volume vs the total quantity of services", 
         x = "Number of services", y = "Volume") +
    geom_label(aes(x = 52, y = 890, label = "Positive\nservice"), 
               label.size = NA,
               size = 4,
               colour = "darkgreen",
               hjust = 0,
               vjust = 0,
               lineheight = 0.8) +
    geom_label(aes(x = 300, y = 525, label = "Negative\nservice"), 
               label.size = NA,
               size = 4,
               colour = "darkred",
               lineheight = 0.8) +
    geom_curve(aes(xend = 35, yend = 1270, x = 100, y = 1450), 
               colour = "darkred",
               size = 0.5, 
               curvature = -0.2, 
               arrow = arrow(length = unit(0.03, "npc"))) +
    geom_label(aes(x = 100, y = 1400, label = "When the number of services start\nto surpass 40 negative services, then\nthe sales start to decrease."),
               label.size = NA,
               size = 4,
               colour = "darkred",
               hjust = 0,
               vjust = 0,
               lineheight = 0.8) +
    geom_text(aes(label = if_else(service_type %in% "Pos_Ser" & 
                                     service_quantity > 40 &
                                     Vol < 1000, ProductType, NULL)),
               size = 4,
               colour = "darkgreen",
               hjust = -0.5,
               vjust = 1.2,
               lineheight = 0, 
               alpha = 0.3) +
    scale_color_manual(values = c("darkgreen","darkred"), 
                       labels = c("Positive service", "Negative\nservice")) +
    theme_classic() +
    theme(axis.text.y = element_text(),
          axis.text.x = element_text(), 
          legend.position = "none")

# taking out the outliers in positive service review
ex_prod_dummy %<>%
  dplyr::filter(!(product_num %in% c("167")))
```

## 4th modalization: linear regression

```{r 4th modlaization}
ex_prod_4mod <- ex_prod_dummy %>% 
  dplyr::select(x2, x4, Pos_Ser, Neg_Ser, Recomend, PC, Laptop, 
                Netb, Smart_Ph, Vol)

# creating trainin and testing with the features selected
set.seed(123)
train_id <- createDataPartition(y = ex_prod_4mod$Vol,
                                p = 0.80,
                                list = F)
train <- ex_prod_4mod[train_id,]
test <- ex_prod_4mod[-train_id,]

# model creation
mod_4lm <- lm(formula = Vol ~., data = train)

# model performance
train_res_mod4 <- postResample(pred = predict(object = mod_4lm, newdata = train),
                             obs = train$Vol)
results_mod4 <- postResample(pred = predict(object = mod_4lm, newdata = test),
                             obs = test$Vol)

# creating a grid with the different results
table_mod4 <- tribble(~metric,   ~train           ,        ~test     , 
                        "RMSE" , round(train_res_mod4[[1]],2), round(results_mod4[[1]],2),      
                        "R^2"  , paste(round(train_res_mod4[[2]]*100,2),"%"), paste(round(results_mod4[[2]]*100,2),"%"))
kable(table_mod4) %>% 
  kable_styling(bootstrap_options = c("hover"), 
                full_width = F, position = "center", fixed_thead = T)
```

The model has improved a little bit. Let's see how is performing to the categories we are interested. 

## 4th error check: error visualization lm {.flexbox .vcenter}

```{r 4th error check, warning=F, message=F}
# looking at the metrics of the relevant categories
ex_prod_dummy %<>%
  add_predictions(model = mod_4lm, var = "pred") %>% 
  add_residuals(model = mod_4lm, var = "resid")

ex_prod_dummy %>% 
  dplyr::filter(ProductType %in% rel_categories) -> ex_prod_filt

metrics_rel_prod <- postResample(pred = ex_prod_filt$pred, obs = ex_prod_filt$Vol)

# error plot
ex_prod_dummy %>% 
  ggplot(aes(x = pred, y = Vol)) +
    geom_point(aes(color = (ProductType %in% rel_categories))) + 
    geom_abline(intercept = 0, slope = 1, color = "darkgray") +
    geom_label(aes(label = if_else(abs(resid)>treshold & 
                              ProductType %in% rel_categories, 
                              paste(ProductType, product_num), NULL)),
               hjust = 0, 
               vjust = 0.4, 
               colour = "red2", 
               fill = NA, 
               label.size = NA, 
               size = 3.5) +
    geom_label(aes(x = -300, y = 2000,
                   label = paste0("The metrics for the relevant product types are:\n   - RMSE: ",round(metrics_rel_prod[[1]],3),"\n   - Rsquared: ",round(metrics_rel_prod[[2]],3),"\n   - MAE: ",round(metrics_rel_prod[[3]],3))),
               label.size = NA,
               size = 4.5,
               colour = "red2",
               hjust = 0,
               vjust = 0.5,
               lineheight = 0.8) +
    labs(title = "Error visualizations 4th model (lm)",
         x = "Predicted volume",
         y = "Volume") +
    scale_color_manual(values = c("grey","red")) +
    theme_classic() +
    theme(axis.text.y = element_text(),
          axis.text.x = element_text(), 
          legend.title = element_blank(), 
          legend.position = "none") -> error_plot_mod4
error_plot_mod4

# removing predictions
ex_prod_dummy$pred <- NULL
ex_prod_dummy$resid <- NULL
```

## 5th modalization: using knn with caret

```{r preparing the train and test 5th modalization}
# creating training and testing 
set.seed(123)
train_id <- createDataPartition(y = ex_prod_dummy$Vol,
                                p = 0.8, 
                                list = F)
train <- ex_prod_dummy[train_id,]
test <- ex_prod_dummy[-train_id,]
```

```{r knn with caret, echo=TRUE, warning=FALSE, message=FALSE}
# defining variables to create the model 
rel_var <- c("x4","x2","Pos_Ser","Neg_Ser","Recomend","Vol","PC","Laptop",
             "Netb","Smart_Ph")

# cross validation
ctrl <- caret::trainControl(method = "repeatedcv",
                            number = 10,
                            repeats = 3)

# modalization 
mod_5knn_caret <- caret::train(Vol ~.,
                               method = "knn",
                               data = train[,rel_var],
                               trControl = ctrl, 
                               preProcess = c("center","scale"))
```

```{r table of errors 5th model}
# model performance
train_res_mod5 <- postResample(pred = predict(object = mod_5knn_caret, 
                                              newdata = train),
                             obs = train$Vol)
results_mod5 <- postResample(pred = predict(object = mod_5knn_caret, 
                                            newdata = test),
                             obs = test$Vol)

# creating a grid with the different results
table_mod5 <- tribble(~metric,   ~train           ,        ~test     , 
                        "RMSE" , round(train_res_mod5[[1]],2), round(results_mod5[[1]],2),      
                        "R^2"  , paste(round(train_res_mod5[[2]]*100,2),"%"), paste(round(results_mod5[[2]]*100,2),"%"))
kable(table_mod5) %>% 
  kable_styling(bootstrap_options = c("hover"), 
                full_width = F, position = "center", fixed_thead = T)
```

## 5th error check: error visualization knn {.flexbox .vcenter}

```{r warning=FALSE, message=FALSE}
# looking at the metrics of the relevant categories
ex_prod_dummy %<>%
  add_predictions(model = mod_5knn_caret, var = "pred") %>% 
  add_residuals(model = mod_5knn_caret, var = "resid")

ex_prod_dummy %>% 
  dplyr::filter(ProductType %in% rel_categories) -> ex_prod_filt

metrics_rel_prod <- postResample(pred = ex_prod_filt$pred, obs = ex_prod_filt$Vol)

# error plot
ex_prod_dummy %>% 
  ggplot(aes(x = pred, y = Vol)) +
    geom_point(aes(color = (ProductType %in% rel_categories))) + 
    geom_abline(intercept = 0, slope = 1, color = "darkgray") +
    geom_label(aes(label = if_else(abs(resid)>treshold & 
                              ProductType %in% rel_categories, 
                              paste(ProductType, product_num), NULL)),
               hjust = 0, 
               vjust = 0.4, 
               colour = "red2", 
               fill = NA, 
               label.size = NA, 
               size = 3.5) +
    geom_label(aes(x = 10, y = 2000,
                   label = paste0("The metrics for the relevant product types are:\n   - RMSE: ",round(metrics_rel_prod[[1]],3),"\n   - Rsquared: ",round(metrics_rel_prod[[2]],3),"\n   - MAE: ",round(metrics_rel_prod[[3]],3))),
               label.size = NA,
               size = 4.5,
               colour = "red2",
               hjust = 0,
               vjust = 0.5,
               lineheight = 0.8) +
    labs(title = paste("Error visualizations 5th model with knn, k =",mod_5knn_caret$bestTune[[1]]),
         x = "Predicted volume",
         y = "Volume") +
    scale_color_manual(values = c("grey","red")) +
    theme_classic() +
    theme(axis.text.y = element_text(),
          axis.text.x = element_text(), 
          legend.title = element_blank(), 
          legend.position = "none") -> error_plot_mod4
error_plot_mod4

# removing predictions
ex_prod_dummy$pred <- NULL
ex_prod_dummy$resid <- NULL
```

## 6th modalization: using Random Forest  {.flexbox .vcenter}

```{r defining relevant variables, echo=TRUE}
set.seed(123)
mod_6rf <- caret::train(Vol ~ .,
                       method = "rf",
                       data = train[,rel_var],
                       trControl = ctrl)
```

```{r table of errors 6th model}
# model performance
train_res_mod6 <- postResample(pred = predict(object = mod_6rf, 
                                              newdata = train),
                             obs = train$Vol)
results_mod6 <- postResample(pred = predict(object = mod_6rf, 
                                            newdata = test),
                             obs = test$Vol)

# creating a grid with the different results
table_mod6 <- tribble(~metric,   ~train           ,        ~test     , 
                        "RMSE" , round(train_res_mod6[[1]],2), round(results_mod6[[1]],2),      
                        "R^2"  , paste(round(train_res_mod6[[2]]*100,2),"%"), paste(round(results_mod6[[2]]*100,2),"%"))
kable(table_mod6) %>% 
  kable_styling(bootstrap_options = c("hover"), 
                full_width = F, position = "center", fixed_thead = T)
```

## 6th error check: error visualization rf {.flexbox .vcenter}

```{r warning=FALSE, message=FALSE}
# looking at the metrics of the relevant categories
ex_prod_dummy %<>%
  add_predictions(model = mod_6rf, var = "pred") %>% 
  add_residuals(model = mod_6rf, var = "resid")

ex_prod_dummy %>% 
  dplyr::filter(ProductType %in% rel_categories) -> ex_prod_filt

metrics_rel_prod <- postResample(pred = ex_prod_filt$pred, obs = ex_prod_filt$Vol)

# error plot
ex_prod_dummy %>% 
  ggplot(aes(x = pred, y = Vol)) +
    geom_point(aes(color = (ProductType %in% rel_categories))) + 
    geom_abline(intercept = 0, slope = 1, color = "darkgray") +
    geom_label(aes(label = if_else(abs(resid)>treshold & 
                              ProductType %in% rel_categories, 
                              paste(ProductType, product_num), NULL)),
               hjust = 0, 
               vjust = 0.4, 
               colour = "red2", 
               fill = NA, 
               label.size = NA, 
               size = 3.5) +
    geom_label(aes(x = 10, y = 2000,
                   label = paste0("The metrics for the relevant product types are:\n   - RMSE: ",round(metrics_rel_prod[[1]],3),"\n   - Rsquared: ",round(metrics_rel_prod[[2]],3),"\n   - MAE: ",round(metrics_rel_prod[[3]],3))),
               label.size = NA,
               size = 4.5,
               colour = "red2",
               hjust = 0,
               vjust = 0.5,
               lineheight = 0.8) +
    labs(title = "Error visualizations 6th model rf",
         x = "Predicted volume",
         y = "Volume") +
    scale_color_manual(values = c("grey","red")) +
    theme_classic() +
    theme(axis.text.y = element_text(),
          axis.text.x = element_text(), 
          legend.title = element_blank(), 
          legend.position = "none") -> error_plot_mod4
error_plot_mod4

# removing predictions
ex_prod_dummy$pred <- NULL
ex_prod_dummy$resid <- NULL
```

## 7th modalization: using Support Vector Machine  {.flexbox .vcenter}

```{r modalization with SVM, echo=TRUE, warning=FALSE, message=FALSE}
set.seed(123)
mod_7svm <- caret::train(Vol ~ .,
                       method = "svmLinear",
                       data = train[,rel_var],
                       trControl = ctrl)
```

```{r creating results table for 7th model}
# model performance
train_res_mod7 <- postResample(pred = predict(object = mod_7svm, 
                                              newdata = train),
                             obs = train$Vol)
results_mod7 <- postResample(pred = predict(object = mod_7svm, 
                                            newdata = test),
                             obs = test$Vol)

# creating a grid with the different results
table_mod7 <- tribble(~metric,   ~train           ,        ~test     , 
                        "RMSE" , round(train_res_mod7[[1]],2), round(results_mod7[[1]],2),      
                        "R^2"  , paste(round(train_res_mod7[[2]]*100,2),"%"), paste(round(results_mod7[[2]]*100,2),"%"))
kable(table_mod7) %>% 
  kable_styling(bootstrap_options = c("hover"), 
                full_width = F, position = "center", fixed_thead = T)
```

## 7th error check: error visualization SVM  {.flexbox .vcenter}

```{r warning=FALSE, message=FALSE}
# looking at the metrics of the relevant categories
ex_prod_dummy %<>%
  add_predictions(model = mod_7svm, var = "pred") %>% 
  add_residuals(model = mod_7svm, var = "resid")

ex_prod_dummy %>% 
  dplyr::filter(ProductType %in% rel_categories) -> ex_prod_filt

metrics_rel_prod <- postResample(pred = ex_prod_filt$pred, obs = ex_prod_filt$Vol)

# error plot
ex_prod_dummy %>% 
  ggplot(aes(x = pred, y = Vol)) +
    geom_point(aes(color = (ProductType %in% rel_categories))) + 
    geom_abline(intercept = 0, slope = 1, color = "darkgray") +
    geom_label(aes(label = if_else(abs(resid)>treshold & 
                              ProductType %in% rel_categories, 
                              paste(ProductType, product_num), NULL)),
               hjust = 0, 
               vjust = 0.4, 
               colour = "red2", 
               fill = NA, 
               label.size = NA, 
               size = 3.5) +
    geom_label(aes(x = 10, y = 2000,
                   label = paste0("The metrics for the relevant product types are:\n   - RMSE: ",round(metrics_rel_prod[[1]],3),"\n   - Rsquared: ",round(metrics_rel_prod[[2]],3),"\n   - MAE: ",round(metrics_rel_prod[[3]],3))),
               label.size = NA,
               size = 4.5,
               colour = "red2",
               hjust = 0,
               vjust = 0.5,
               lineheight = 0.8) +
    labs(title = "Error visualizations 6th model rf",
         x = "Predicted volume",
         y = "Volume") +
    scale_color_manual(values = c("grey","red")) +
    theme_classic() +
    theme(axis.text.y = element_text(),
          axis.text.x = element_text(), 
          legend.title = element_blank(), 
          legend.position = "none") -> error_plot_mod4
error_plot_mod4

# removing predictions
ex_prod_dummy$pred <- NULL
ex_prod_dummy$resid <- NULL
```

## Model application and results  {.flexbox .vcenter}

```{r preparing the new products dataset}
new_prod$ProductType <- factor(new_prod$ProductType)
new_prod %<>% 
  fastDummies::dummy_columns(remove_first_dummy = FALSE) %>% 
  select(ProductType_PC,ProductType_Laptop,ProductType_Netbook,
         ProductType_Smartphone,x4StarReviews,x2StarReviews,
         PositiveServiceReview,NegativeServiceReview,Recommendproduct,
         Volume,ProductType,ProductNum,ProfitMargin, Price) %>% 
  rename(PC = ProductType_PC, 
         Laptop = ProductType_Laptop,
         Netb = ProductType_Netbook,
         Smart_Ph = ProductType_Smartphone, 
         x4 = x4StarReviews,
         x2 = x2StarReviews, 
         Pos_Ser = PositiveServiceReview, 
         Neg_Ser = NegativeServiceReview,
         Recomend = Recommendproduct,
         Vol = Volume,
         product_num = ProductNum) %>% 
  mutate(data_type = "new_products")
new_prod$product_num <- as.character(new_prod$product_num)
```


```{r}
best_new <- new_prod %>% 
  add_predictions(model = mod_6rf, var = "Vol") %>% 
  select(ProductType, product_num, Vol, ProfitMargin, Price) %>% 
  filter(ProductType %in% rel_categories) %>% 
  mutate(Total_Profits = ProfitMargin*Vol*Price, 
         Total_Profits_Dol = paste(round((Total_Profits), 0),"$"),
         type_num = paste(ProductType, product_num)) %>% 
  arrange(Total_Profits)

best_new_position <- unique(best_new$type_num)

best_new %>% 
  mutate(category_prodNum = paste(ProductType, product_num)) %>% 
  ggplot(aes(x = reorder(category_prodNum, Total_Profits))) +
    geom_col(aes(y = Total_Profits), 
             fill = "gold") +
    geom_col(aes(y = -Vol), 
             fill = "dodgerblue3") +
    coord_flip() +
    scale_y_continuous(limits = c(-5000, 100000), labels = NULL) +
    geom_label(aes(x = paste(ProductType, product_num),
                   y = Total_Profits, 
                   label = Total_Profits_Dol),
               hjust = 0, 
               vjust = 0.4, 
               colour = "goldenrod3", 
               fill = NA, 
               label.size = NA, 
               size = 3.5) +
    geom_label(aes(x = paste(ProductType, product_num),
                   y = -Vol, 
                   label = round(Vol, 0)),
               hjust = 1, 
               vjust = 0.4, 
               colour = "dodgerblue4", 
               fill = NA, 
               label.size = NA, 
               size = 3.5) +
    scale_x_discrete(limits = best_new_position) +
    labs(title = "Predicitng sales of new products",
         subtitle = "Pred.Volume (items) vs Pred.Profits ($) for Random Forest model") +
    theme(legend.position = "bottom", 
          legend.title = element_blank(), 
          plot.title = element_text(hjust = 0.5), 
          plot.subtitle = element_text(hjust = 0.5)) + theme_void() -> p1
p1 + theme(axis.title.x = element_blank(), 
           axis.title.y = element_blank(), 
           axis.text.y = element_text())
```

