---
title: "Multiple regression in R"
author: "Joan Claverol"
date: "31 de marzo de 2019"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r loading libraries and dataset, message=FALSE, warning=F}
if(require("pacman")=="FALSE"){
  install.packages("pacman")
} 

pacman::p_load(corrplot, tidyverse, caret, dunn.test, Hmisc,xtable, htmlTable, 
               partykit, knitr, kableExtra, dummies, RColorBrewer, e1071, gbm)

ExProd <- read_csv("../data/existingproductattributes2017.2.csv")
NwProd <- read_csv("../data/newproductattributes2017.2.csv")
```


## Task overview

What data do we have? New product attributes and existing product attributes.

- Predicting sales of four different product types: PC, Laptops, Netbooks and Smartphones
- Assessing the impact services reviews and customer reviews have on sales of different product types

## Index

* Data cleaning

* Data exploration

* Pre-process: feature selection (correlation matrix) & feature engineering

* Modalization: linear regresion, KNN, SVM, Random forest, GBM

* Error analysis

## Data cleaning

Transformation to factor:

```{r transformation to factors}
fact_var <- c("ProductType","ProductNum")
ExProd[fact_var] <- apply(ExProd[fact_var], 2, as.factor)
```


## Data cleaning: missing values

```{r looking for NAs}
# looking for NAs
kable(ExProd[is.na(ExProd$BestSellersRank),]) %>% 
  kable_styling(bootstrap_options = "responsive", font_size = 13) %>%
  scroll_box(width = "100%", height = "500px")
ExProd$BestSellersRank <- NULL
```

## 1st data expl.: Blackwell business

```{r business overview, warning=F}
# Is the volume related to the categories?

ExProd %>%
  group_by(ProductType) %>%
  summarise(Total_Volume = sum(Volume)) %>%
  arrange(desc(Total_Volume)) -> Volume_category

# Number of products by category

ExProd %>%
  group_by(ProductType) %>%
  summarise(Number_Products = n()) %>%
  arrange(desc(Number_Products)) -> NumProd_category

# Profit per category

ExProd %>%
  group_by(ProductType) %>%
  summarise(Mean_Profit_Perc = round(mean(ProfitMargin),2)) %>%
  arrange(desc(Mean_Profit_Perc)) -> Profit_category

# # Show the information into one table
# kable(Profit_category %>%
#         left_join(NumProd_category, by = 'ProductType') %>%
#         left_join(Volume_category, by = 'ProductType') %>%
#         mutate(Total_Profits = Mean_Profit_Perc*Total_Volume) %>% 
#         arrange(desc(Total_Profits)) %>% 
#         mutate(Total_Profits = paste0(Total_Profits, " €")),
#       col.names = c("", "Profit", "Nº products", 
#                     "Total Volume", "Total Profits")) %>% 
#   kable_styling(bootstrap_options = "responsive", font_size = 14) %>% 
#   column_spec(1, bold = T, include_thead = T) %>% 
#   column_spec(5, background = "#f0f5f0")

# Create a graph to understand 
Profit_category %>%
  left_join(NumProd_category, by = 'ProductType') %>%
  left_join(Volume_category, by = 'ProductType') %>%
  mutate(Total_Profits = Mean_Profit_Perc*Total_Volume) %>% 
  arrange(Total_Profits) %>%
  ggplot(aes(x = reorder(ProductType, Total_Profits))) +
    geom_col(aes(y = -Total_Profits), fill = "dodgerblue3") +
    geom_col(aes(y = Total_Volume), fill = "gold") +
    coord_flip() +
    scale_y_continuous(limits = c(-5000,27000), labels = NULL) +
    geom_label(aes(x = ProductType, y = -Total_Profits, 
                   label = round((Total_Profits), 0)),
               hjust = 1, 
               vjust = 0.5, 
               colour = "dodgerblue3", 
               fill = NA, 
               label.size = NA, 
               size = 3) +
    geom_label(aes(x = ProductType, y = Total_Volume, 
                   label = round(Total_Volume, 0)),
               hjust = 0, 
               vjust = 0.5, 
               colour = "goldenrod3", 
               fill = NA, 
               label.size = NA, 
               size = 3) +
    labs(title = "Total Profits vs Total Volume") +
    theme(legend.position = "bottom", 
          legend.title = element_blank(), 
          plot.title = element_text(hjust = 0.5), 
          plot.subtitle = element_text(hjust = 0.5)) + theme_minimal() -> p1
p1 + theme(axis.title.x = element_blank(), 
           axis.title.y = element_blank())
  
```


## 1st modalisation: linear regression

```{r train and test creation, warning=F, message=F}
set.seed(123)
train_id <- createDataPartition(y = ExProd$Volume,
                                p = 0.75, 
                                list = F)
train <- ExProd[train_id,]
test <- ExProd[-train_id,]

# giving product number to row names
rownames(test) <- test$ProductNum
rownames(train) <- train$ProductNum

# model with linear regression
mod_lm <- lm(formula = Volume ~ ., data = train)

```

## 1st error check: error visualization

```{r warning=F, message=F}
# par(mfrow = c(2,2))
# plot(mod_lm)
# par(mfrow = c(1,1))
```

```{r}
# postResample(pred = predict(object = mod_lm, newdata = test),
#              obs = test$Volume)
```

